Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-23 TACAS2018/paper.tex
+comments for the experimental section

The models we consider have two sources of error that are due to numerical  
representation which we commonly refer to as the FWL effect.
The first is the numerical error introduced by the
fixed-point numbers employed to model the plant, i.e., to represent the
plant dynamics $A_d$, $B_d$, $C_d$, $D_d$, $x_k$ and $y_k$.
The second is the quantization error
introduced by the digital controller, which performs operations on
fixed-point numbers.  In this section we outline the notation for the
representation of numbers, and briefly describe the errors
introduced.  A~formal discussion is in
Appendix~\ref{sec:numeric_rep}.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Modeling quantization as noise} \label{sec:quantization-noise}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
In Figure \ref{fig:observersystem2} we introduced
several sources of noise, which are due to quantization effects. We now describe
their nature and create a sound model for them to be used during our synthesis
and verification process.

@@

The benchmark suite employed to evaluate the proposed technique is 
composed by 7 SISO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
In order to obtain statistically relevant results, we have taken these models
and modified each possible combination of their parameters by a 10\% tolerance,
thus creating hundreds of different benchmarks from this base.
In the verification module, we have used the tool Axelerator~\cite{} .

%-------------------------------
\subsection{Results}
\label{exp:results}
%-------------------------------
\begin{table}
\centering
\footnotesize
%
\begin{tabular}{| r | l | c | c | r | r | r | r | r | r | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{count} & \multicolumn{2}{|c|}{CEGIS ($\mat{K}$)} & \multicolumn{5}{|c|}{CEGORS($\mat{K}+\mat{L}+T_s$)} \\
   &                                 & & & \multicolumn{1}{|c|}{-AR1} & \multicolumn{1}{|c|}{-OR} & \multicolumn{1}{|c|}{-AR2} & \multicolumn{1}{|c|}{-OR} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
1  & DC Motor          & 2 & 10 & 9.5\,s & 2.1\,s& 1.9\,s& 3.4\,s& 1.2\,s &   3.1\,s &   14.1\,s\\
2  & Helicopter        & 3  & 10 & \xmark & 1.4\,s& \xmark & \xmark & 6.7\,s  &   18.9\,s & \xmark\\
3  & Inverted Pendulum & 4 & 10 &   9.7\,s &   0.6\,s& \xmark &112.6\,s& 12.0\,s  &  18.1\,s &  414.0\,s\\
4  & Magnetic Pointer  & 2  & 10 & \xmark & 44.1\,s& \xmark & \xmark& 4.6\,s  &  39.0\,s &  \xmark \\
%5 & Magnetic Suspension          & 2 & 1 & 12.2\,s& 0.6\,s & & & N/A  &   N/A &   N/A\\
5  & Pendulum          & 2 & 10 & 14.0\,s & 0.6\,s& 2.0\,s & 1.5\,s &1.2\,s  &   1.5\,s &   4.3\,s\\
6  & Suspension        & 4 & 10 & 73.7\,s& 48.3\,s & \xmark & 110.2\,s &24.0\,s  &   46.1\,s &  557.9\,s\\
7  & Tape Driver       & 3 & 10 & 10.1\,s& 12.4\,s& 140.3\,s &10.5\,s &2.6\,s  &   10.5\,s &   104.6\,s\\
%9 & Satellite          & 2 & 1 & 9.4\,s& 0.7\,s & & & N/A  &   N/A &   N/A\\
%   & Total                 &   & 2002 & & & & & 1.2\,s & 16.1\,s & 876.8\,s\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{\label{tab:cegis_results}
Experimental results. All times are median (except for Min and Max). \xmark~indicates failure to find a controller (in the median case it means that more than half of the times we failed to find a controller), either due to timeout or insufficient numeric precision (bitvectors are limited to 64bits). -AR1 is standard CEGIS, -AR2 uses Solution Generalization but no refinement. -OR means Abstraction Refinement but no optimization refinement.}
\end{table}

>>>>

The models we consider have two sources of error that are due to numerical  
representation which we commonly refer to as FWL effects.
The first is the numerical error introduced by the
fixed-point numbers employed to model the plant, i.e., to represent the
plant dynamics $A_d$, $B_d$, $C_d$, $D_d$, $x_k$ and $y_k$.
The second is the quantization error
introduced by the digital controller, which performs operations on
fixed-point numbers.  In this section we outline the notation for the
representation of numbers, and briefly describe the errors
introduced.  A~formal discussion is in
Appendix~\ref{sec:numeric_rep}.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Modeling quantization as noise} \label{sec:quantization-noise}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\note{Add a summary sentence and move the rest to the appendix.}
In Figure \ref{fig:observersystem2} we introduced
several sources of noise, which are due to quantization effects. We now describe
their nature and create a sound model for them to be used during our synthesis
and verification process.

@@

The benchmark suite employed to evaluate the proposed technique is 
composed by 7 SISO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
In order to obtain statistically relevant results, we have taken these models
and modified each possible combination of their parameters by a 10\% tolerance,
thus creating hundreds \note{how many?} of different benchmarks from this base.
In the verification module, we have used the tool Axelerator~\cite{} .

%-------------------------------
\subsection{Results}
\label{exp:results}
%-------------------------------
\note{Start with a description of the results, e.g. ``We managed to synthesise controllers in X of the cases. Average time ... In the rest of the cases ...''}.

\note{In order to show the improvements due to our optimization-enhanced CEGIS, we also compared our approach against a standard CEGIS procedure..}

\note{remove some of the subcases of CEGIS and CEGORS. Those that are still used need to be explained in the actual section, not in the table's caption.}

\begin{table}
\centering
\footnotesize
%
\begin{tabular}{| r | l | c | c | r | r | r | r | r | r | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{count} & \multicolumn{2}{|c|}{CEGIS ($\mat{K}$)} & \multicolumn{5}{|c|}{CEGORS($\mat{K}+\mat{L}+T_s$)} \\
   &                                 & & & \multicolumn{1}{|c|}{-AR1} & \multicolumn{1}{|c|}{-OR} & \multicolumn{1}{|c|}{-AR2} & \multicolumn{1}{|c|}{-OR} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
1  & DC Motor          & 2 & 10 & 9.5\,s & 2.1\,s& 1.9\,s& 3.4\,s& 1.2\,s &   3.1\,s &   14.1\,s\\
2  & Helicopter        & 3  & 10 & \xmark & 1.4\,s& \xmark & \xmark & 6.7\,s  &   18.9\,s & \xmark\\
3  & Inverted Pendulum & 4 & 10 &   9.7\,s &   0.6\,s& \xmark &112.6\,s& 12.0\,s  &  18.1\,s &  414.0\,s\\
4  & Magnetic Pointer  & 2  & 10 & \xmark & 44.1\,s& \xmark & \xmark& 4.6\,s  &  39.0\,s &  \xmark \\
%5 & Magnetic Suspension          & 2 & 1 & 12.2\,s& 0.6\,s & & & N/A  &   N/A &   N/A\\
5  & Pendulum          & 2 & 10 & 14.0\,s & 0.6\,s& 2.0\,s & 1.5\,s &1.2\,s  &   1.5\,s &   4.3\,s\\
6  & Suspension        & 4 & 10 & 73.7\,s& 48.3\,s & \xmark & 110.2\,s &24.0\,s  &   46.1\,s &  557.9\,s\\
7  & Tape Driver       & 3 & 10 & 10.1\,s& 12.4\,s& 140.3\,s &10.5\,s &2.6\,s  &   10.5\,s &   104.6\,s\\
%9 & Satellite          & 2 & 1 & 9.4\,s& 0.7\,s & & & N/A  &   N/A &   N/A\\
%   & Total                 &   & 2002 & & & & & 1.2\,s & 16.1\,s & 876.8\,s\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{\label{tab:cegis_results}
Experimental results. All times are median (except for Min and Max). \xmark~indicates failure to find a controller (in the median case it means that more than half of the times we failed to find a controller), either due to timeout or insufficient numeric precision (bitvectors are limited to 64bits). -AR1 is standard CEGIS, -AR2 uses Solution Generalization but no refinement. -OR means Abstraction Refinement but no optimization refinement.}
\end{table}
